Networked Character Devices

### 2011-12-11 report/paper.tex
Added Potnetial Uses and Conclusion, Fixed rng.svg server<->client mistake

The current NCD system only support a single device per server and per
client. To be truly useful and to enable the construction of the
kinds of system we envision NCD being used for (Section
\ref{potentialuses}), we must at least
expand the client-side
system to support importing an arbitrary number of devices from one
or more servers. Ideally, servers should also be capable of serving
multiple devices, but this is of less importance than multi-device
client handling.

@@

@@

@@

@@

@@

@@

>>>>

The current NCD system only support a single device per server and per
client. To be truly useful and to enable the construction of the
kinds of system we envision NCD being used for (Section
\ref{sec:potentialuses}), we must at least
expand the client-side
system to support importing an arbitrary number of devices from one
or more servers. Ideally, servers should also be capable of serving
multiple devices, but this is of less importance than multi-device
client handling.

@@

The shift from the traditional concept of locally available devices to a
broader concept of generalized network accessible devices has the
potential to allow the creation of a variety of novel
applications. Here we explore a few of the possible applications of an
NCD system.

@@

KVM (Keyboard-Video-Mouse) systems are commonly used in data centers
and other areas where a user wishes to use a single keyboard, video,
and mouse, to control multiple machines. KVM systems range from simple KVM
switches that allow the user to select which local machine is
physically connected to his or her i/o devices to
networked KVM systems that allow the user to use a
local KVM setup to interface with a computer located elsewhere on the
network. The latter class of networked KVM devices traditionally require
expensive propriety hardware.

@@

As Figure \ref{fig:kvm} shows, we can use Networked Character Devices
to quickly and easily build a networked KVM system in software,
forgoing the need for expensive specialized hardware. The user simply
connects a spare mouse and keyboard to an NCD server, tells the NCD
system to export these devices, and then imports them on the client
machine (s)he wishes to control. To the client, the devices appear as
a locally connected keyboard and mouse, and the user may issue input to
the client machine via the keyboard and mouse connected to the
server.

As we mentioned previously, an NCD based KVM system would require the
appropriate import interface to the Linux HID subsystem, but once this is
in place, building a networked KVM atop the NCD system would be a
rather trivial matter.

@@

Another example of the novel systems that can be built use Network
Charter Devices is a distributed random number generator. Linux has a
fairly robust random number generator built into it and accessible as
a Character Device at \texttt{/dev/random}. This RNG relies on the
local entropy pool (generally filled by human interaction, interrupt
timings, and other high entropy events) to generate random
numbers. This, the speed at which random numbers can be generated is
limited on any single system to the locally available
entropy. This can severely hinder the
performance of systems that require random numbers\footnote{Linux also
provides the \texttt{/dev/urandom} RNG which is a pseudorandom number
generator seeded off teh true
\texttt{/dev/random}. \texttt{/dev/urandom} trades ``randomness'' in
favor of speed. It is thus handy when one just needs to quickly
generate pseudorandom numbers, but is not appropriate for cryptography or
other secure random system.}.

@@

We can imagine a system that uses Network Character Devices to overcome
the normal limitations related to relying on locally available entropy. This
system would be capable of generating cryptographically secure
randomness while also delivering high performance.

Figure \ref{fig:rng} shows how such a system might work. In this
distributed RNG system, multiple hosts act as NCD servers by exporting
their local \texttt{/dev/random} character devices. These devices are
all imported by a single client running some from on RNG aggregator
that combines the relatively slow output form the local RNGs into a
single high speed RNG output. We can effectively pool the entropy
available on numerous hosts to drive a single high performance RNG
system.

As in the KVM system, using Networked Character Devices makes the
implementation of such a system relatively straight forward.

@@

Network Character Devices provide an extension of the standard device
driver file interface across the network. They allow for device
capabilities to be exported from where they are not needed and imported
where they are. By separating device usage from the device physical
location and host, the NCD system provides a generalized, transparent,
means for abstracting device functionality across a network.

As the potential uses demonstrate, the power of
the NCD concept is in the ability to achieve complex solutions without
needing to resort to specialized device networking protocols and other
complex ad-hoc systems. We hope to continue the development of the NCD
concept and to utilize it to build powerful, but easily implementable,
device-dependent systems.
